Capstone Movielens Report

### 2025-02-02 reports/capstone-movielens-report.Rmd
Alternative citing experiment.

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
#bibliography: references.bib
#csl: bit-numerical-mathematics.csl 
output:
  pdf_document: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true
    citation_package: biblatex

@@

The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
Following the _Netflix Grand Prize Contest_`r # \cite{knuthwebsite}` `r citeB("NYT1MNP")`  requirements, we will evaluate the RMSE score defined as`r citeB("IDS2_23-2")`:

@@

```{r results = "asis", echo = FALSE}
# \addcontentsline{toc}{section}{References} 
#\printbibliography[title={Whole bibliography}]
# 
# \color{black}
# \bibliography{references}
# \bibliographystyle{mla-good}
#\bibliographystyle{mla-good}
#\bibliographystyle{is-unsrt}
#\bibliographystyle{is-plain}
#\bibliographystyle{is-abbrv}
#\bibliographystyle{apalike}

PrintBibliography(bib,
                  .opts = list(check.entries = FALSE,
                               hyperlink = "to.bib",
                               first.inits = FALSE,
                               bib.style = "numeric",
                               style = "markdown",
                               cite.style = 'numeric'))

>>>>

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
#bibliography: references.bib
#csl: bit-numerical-mathematics.csl 
output:
  pdf_document: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true
    #citation_package: biblatex

@@

The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
Following the _Netflix Grand Prize Contest_ \cite{NYT1MNP} `r #\cite{knuthwebsite}` `r #citeB("NYT1MNP")`  requirements, we will evaluate the RMSE score defined as`r citeB("IDS2_23-2")`:

@@

\addcontentsline{toc}{section}{References}
 \color{black}
\bibliography{references}
\bibliographystyle{mla-good}

```{r results = "asis", echo = FALSE}
# \addcontentsline{toc}{section}{References}
# \printbibliography[title={Whole bibliography}]
# 
# \color{black}
# \bibliography{references}
#\bibliographystyle{mla-good}
#\bibliographystyle{is-unsrt}
#\bibliographystyle{is-plain}
#\bibliographystyle{is-abbrv}
#\bibliographystyle{apalike}

# PrintBibliography(bib,
#                   .opts = list(check.entries = FALSE,
#                                hyperlink = "to.bib",
#                                first.inits = FALSE,
#                                bib.style = "numeric",
#                                style = "markdown",
#                                cite.style = 'numeric'))
